On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2015-11-25 MS.tex
Response to reviwer: change done in results part and discussion

The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately replacing themselves with offspring. An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx}. From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

@@

\textbf{Effect on absolute and relative growth rates}
Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR). According to the growth model, the predicted relationship between growth and SM in seedlings reverts if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}). The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$. For SLA, WD, Hmax and Aarea the predicted relationships are not affected by the growth measurement used.

@@

We first developed a snapshot of the literature, to assess potential to recover useful data from the wide corpus of literature available. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.

@@

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Ultimately data was included from 112 different articles (starred references in bibliography). Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g. fertilization, shade, salt stress). To minimise publication bias via selective reporting of significant results within the published articles (e.g. a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}), we asked those authors reporting a non-significant correlation for additional information about the specific correlation coefficient when this was not provided.

@@

To measure of effect size, we used the cross-species Pearson product-moment correlation coefficient $r$ between growth rate and trait, weighted by the number of species contributing to the relationship. For studies that reported another coefficient -- such as coefficient of determination, Spearman's rho rank correlation, or Kendall's tau rank correlation -- we converted these to correlation coefficients following \citet{Lajeunesse:2013tm}. As the magnitude of Pearson's correlation coefficient approaches $\pm$ 1.0, its distribution becomes skewed. Accordingly, we transformed the correlation $r$ into a metric $z$ with more-desirable statistical properties. The transformation was achieved via Fisher's z-transformation,
\[ z = \frac{1}{2} \ln \frac{1+r}{1-r}, \]
which has a variance estimate of
\[ v_z= \frac{1}{n-3}, \]
where $n$ is the number of species. We weighted effect size by the number of species used to calculate the correlation, instead of the raw number of individuals, because our questions primarily concerned the correlation between growth and traits across species and not within species.

@@

\subsubsection*{Sensitivity analysis}\label{sensitivity-analysis}

We tested how robust our results were to the particular decisions made in the analysis.
In particular, we tested the sensitivity of our results to inclusion of studies that measured a large number of responses for the same trait. The idea is to check that our results were not generated by the dominance of one or few studies reporting several values for the same trait. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size. This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.
We also tested whether the criteria used for including a study in the analysis influenced our results. In addition to the chosen criteria, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Thus we stratified the data set into two subsets: one including only studies under unstressed conditions ('ideal' dataset), and the other set including studies under all conditions ('complete' dataset). We excluded from the ''ideal'' dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for SM (i.e. seed stage), or Hmax (i.e. adult stage).

@@

\cite{Koricheva:2014ku} outlined 14 methodological quality criteria to ensure robust results from meta-analyses. Table \ref{tab:meta} outlines how we addressed each of these. In particular, we quantified heterogeneity in effect size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).

@@

@@

For WD, results were consistent with negative correlations with RGR across all plant sizes (Fig. \ref{fig:fig3} b, model fit not improved when stage was incorporated). Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 2 respectively), meaning a good consistency in the coefficient reported for each stage across studies.

For both Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits. Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions. 
For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached. Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$). At sapling stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig. \ref{fig:fig3} c, and confident intervals overlapping), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies. We could not distinguish between these alternatives. 
As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero). Hovever, the correlation between seed mass and RGR at adult and saling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig. \ref{fig:fig3} c). Again we could not distinguish between these alternatives. But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in coefficients of correlation reported rather than to a much smaller numbers of replicate.

For Aarea, results were consistent with a positive correlation with RGR at seedling stage. However, no conclusion can be drawn about a change along plant stages; only four correlation coefficients were reported for this trait, and three of them were measured at the seedling stage.

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results, or if additional data could reinforce some of our conclusions.

@@

The results reported above were obtained using an even more conservative dataset ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and controlling for the source of trait and growth (i.e. both had to be measured on the same stage). The ''complete'' dataset ($n = 216$) also included correlations measured with absolute growth rate, across two to 10 species, under stressed conditions, and spanning different plant stages between the growth and trait measurements. The release of criteria enlarged in a considerable extent the number of replicates. While some trait-stage combinations were particularly well studied with 59 correlation coefficient reported for SLA at seedling stage, other still showed weak support. Indeed, on the 13 traits-stage combinations studied here, six were supported by five or less correlations coefficient (i.e. WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling).

This ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD and Hmax, and led to similar conclusions (Fig. \ref{fig:fig4}). While the correlation between growth and WD at seedling stage was still negative, the upper CI 95\% was very closed from zero (lower CI: -0.065) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct}; these correlations unlike others used values of WD from adult plants together with growth from seedlings.

For seed mass and Aarea, results from the ''complete'' dataset were even more consistent with expectations from the model. For seed mass, the correlation with RGR was undoubtly not significantly different from zero at adult stage (Fig \ref{fig:fig4}; CI for seedling and adult stages were not overlapping anymore, and model fit improved when stage was incorporated (see log likelihood ratio tests, Fig. \ref{fig:fig4 d}. For Aarea, results were consistent with expectation of positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero). The comparison of effect size between conservative dataset (Fig. \ref{fig:fig3 d}) and complete (Fig. \ref{fig:fig4 d} showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 8 correlations measured under low light conditions were added.

@@

For WD the meta-analysis showed negative correlation with growth across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=2-5). In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.

@@

Meta-analysis showed a positive correlation between Hmax and growth for adult stage, but not for saplings and seedlings. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g. \citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}). In \citet{Wright:2010tp}, Hmax was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees. In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
a) age, b) height and c) diameter. Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth. Study IDs correspond to the reference number in our dataset. Colours denote stage information given by the authors. The solid vertical lines indicate the thresholds used in our analysis. "*" indicated when a stage reassignment is needed. "+" on left side of the graph indicate cases where plants came from different growth form. Results shown here are the ''complete'' dataset (see methods for details).}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait. Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the model including stage effect fitted the data better than the null model. Results shown are from correlation coefficients measured for RGR exclusively, with > 10 species, under unstressed conditions and for a controled trait source (see methods for details).}
\label{fig:fig3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
\caption{The relationships between growth rates and traits along plant stage are not overcasted by experimental conditions (i.e. growth measurement used, environemental conditions, trait source or number of species used to draw the correlation). Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the model including stage effect fitted the data better than the null model. Results shown are from the ''complete dataset'' (see methods for details).}
\label{fig:fig3}
\end{figure}

>>>>

The phrase ``plant ecological strategy'' refers to how species face common challenges of acquiring sufficient water, nutrients and light for growth, and then ultimately replacing themselves with offspring. An idea that species strategy differences might involve fast versus slow growth goes back at least to \citet{Grime:1975gr}, who measured a wide spread of relative growth rates for seedlings during early exponential growth under favourable conditions. Seedling potential relative growth rate (RGR) has continued to be used as a major strategy indicator within the CSR (Competitor - Stress tolerator - Ruderal) classification (e.g. \citealt{grime1979plant, Grime:1997wm}). Meanwhile partitioning of seedling RGR into different components showed that specific leaf area (SLA = 1/leaf mass per area LMA) was typically the strongest source of variation between species \citep{Poorter:1989tx, Rees:2010gk}. From the 1990s a new style of ``trait ecology'' arose whereby measurable traits including SLA were used directly as strategy axes \citep{Westoby:2002ft}. An approach via measurable traits made broad comparisons possible across continents and latitudes and thousands of species. Since then, traits have been seen as constructive approaches to understanding plant growth strategies \citep{Grime:1977kc,Chapin:1980gz}, community composition \citep{Lavorel:2002ff,Shipley:2006ie}, global vegetation dynamics \citep{Scheiter:2013ed} and ecosystem processes \citep{Lavorel:2002ff}.

@@

\textbf{Effect on absolute and relative growth rates}
Tree growth in diameter, height or mass can be expressed in either absolute (AGR) or relative terms (RGR). According to the growth model, the predicted relationship between growth and SM in seedlings reverses if absolute AGR$_\textrm{mass}$ is used instead of RGR$_\textrm{mass}$ (see Appendix \ref{sec:growth}). The correlation with RGR$_\textrm{mass}$ is negative but becomes positive with AGR$_\textrm{mass}$. For SLA, WD, Hmax and Aarea the predicted relationships are not affected by the growth measurement used.

@@

We first developed a snapshot of the literature, to assess the potential to recover useful data from the wide corpus of literature available. This snapshot was obtained via Web of Science database (Thomson Reuters), between March and June 2014, using a range of Boolean search terms in English. Search terms were as follows: (``trait'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), where ``trait'' was allowed to be any of the trait names listed in Table \ref{tab:lit_search}. This snapshot indicated that 82\% of the reported correlations linking growth to any of our five core traits would be recovered by searching only on SLA and WD, allowing us to narrow our search considerably.

@@

Each study had to meet some basic criteria to be included in our analysis. We restricted our meta-analysis to documents reporting: i) the relationship between growth and trait as a correlation coefficient, ii) the sample size and the number of species used to perform the correlation, and iii) the size/stage of plants. Ultimately data was included from 112 different articles (starred references in bibliography). Where available, we also recorded the geographic coordinates, number of sites, experiment type (greenhouse, field experiment, forest, shade-house etc.), growth measure (relative or absolute growth rate measured using plant diameter, height or mass), vegetation type, life form (tree, woody or mixed with herbaceous species etc.), biological scale (interspecific, intraspecific or intragenus), and experimental treatments (e.g. fertilization, shade, salt stress).  We asked the authors reporting a non-significant correlation for additional information about the specific correlation coefficient value when this was not provide. This allowed us to minimise publication bias via selective reporting of significant results within the published articles (e.g. a particular case of a ``failure to publish bias'' see \citealt{Jennions:2013ta}).

@@

To measure of effect size, we used the cross-species Pearson product-moment correlation coefficient $r$ between growth rate and trait, weighted by the number of species contributing to the relationship. For studies that reported another coefficient -- such as coefficient of determination, Spearman's rho rank correlation, or Kendall's tau rank correlation -- we converted these to correlation coefficients following \citet{Lajeunesse:2013tm}. As the magnitude of Pearson's correlation coefficient approaches $\pm$ 1.0, its distribution becomes skewed. Accordingly, we transformed the correlation $r$ into a metric $z$ with more-desirable statistical properties. The transformation was achieved via Fisher's z-transformation,
\[ z = \frac{1}{2} \ln \frac{1+r}{1-r}\]
which has a variance estimate of
\[ v_z= \frac{1}{n-3}\]
where $n$ is the number of species. We weighted effect size by the number of species used to calculate the correlation, instead of the raw number of individuals, because our questions primarily concerned the correlation between growth and traits across species and not within species.

@@

\subsubsection*{"Ideal" vs "complete" dataset}\label{ideal-vs-complete-dataset}

In addition to the chosen criteria for the meta-analyses, the growth measurement used (relative growth rate-RGR or absolute growth rate-AGR), the number of species, the experimental conditions (stressed vs unstressed), and the concordance between stage used to measure trait and growth are clear criteria for assessing the quality of the data for addressing our hypotheses. Thus we stratified the data set into two subsets: one including only studies on RGR, under unstressed conditions and measuring a correlation coefficient at least across 10 species (’ideal’ dataset), and the other set including studies under all conditions (’complete’ dataset). We excluded from the ”ideal” dataset studies where growth and traits were measured on plants from different stages, unless a particular stage was by definition required to measure the trait, such as for SM (i.e. seed stage), or Hmax (i.e. adult stage).

@@

\cite{Koricheva:2014ku} outlined 14 methodological quality criteria to ensure robust results from meta-analyses. Table \ref{tab:meta} outlines how we addressed each of these. In particular, we quantified heterogeneity in effect size, we tested for publication bias and we explored temporal change in effect size (see Appendix \ref{app:supp_info_analyses}).
We also tested how robust our results were to the decisions made in the analysis. In particular, we tested the sensitivity of our results to inclusion of studies that measured a same trait-growth correlation across different conditions (e.g. vegetation type, sites, environemental conditions). The idea is to check that our results were not generated by the dominance of one or few studies reporting several values for the same trait. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and then re-calculated the effect size. This produced a reduced dataset, where multiple responses for any given trait were condensed into a study-level average.

@@

A few number of study reported a trait-growth correlation and meet our basic criteria (112 articles, $n = 216$). The main results reported here were obtained with a conservative approach ($n = 98$), and were thereby confined to correlations with RGR, across at least 10 species, under non-stressed conditions, and for which the source of trait and growth was controlled (i.e. "ideal" dataset).

@@

For WD, Hmax and seed mass, correlations with RGR were also consistent with expectations, although with limitations arising from very unequal numbers of observations between growth stages for some traits. Indeed, confidence intervals of r often spanned zero especially where there were small numbers of studies for particular growth stages, precluding strong conclusions. 
For WD, results were consistent with negative correlations with RGR across all plant sizes (Fig. \ref{fig:fig3} b, model fit not improved when stage was incorporated). Note that the confident intervals were not crossing zero for sapling and seedling stage despite small sample sizes (n= 4 and 2 respectively), meaning a good consistency in the coefficient reported for each stage across studies.

For Hmax, the expectation was for a correlation with growth to be absent for small plants but present at larger sizes, the mechanism being increased relative allocation to reproduction as Hmax is approached. Indeed Hmax was positively correlated with growth at adult stage ($\bar{r}= 0.38 \pm 0.05$). At sapling stages, the correlation between Hmax and growth was not significantly different from that observed at adult stage (model fit not improved when stage was incorporated, see log likelihood ratio tests in Fig. \ref{fig:fig3} c, and confident intervals overlapping), but also was consistent with no correlation (Fig \ref{fig:fig3} c, confidence intervals overlapping zero), due to much smaller numbers of replicate studies. We could not distinguish between these alternatives.

As expected for seed mass, the correlation with RGR shifted from negative at seedling stage ($\bar{r}= -0.5 \pm 0.07$) to not significantly different from zero at adult and sapling stages (Fig \ref{fig:fig3} c, confidence intervals overlapping zero). Hovever, the correlation between seed mass and RGR at adult and saling stages were also not significantly different from that observed at seedling stage (see log likelihood ratio tests and confident intervals overlapping in Fig. \ref{fig:fig3} c). Again we could not distinguish between these alternatives. But unlike Hmax, the number of coefficent reported for seed mass was almost similar between adult (n= 7) and seedling (n= 10) stages, suggesting that confident interval overalapping zero at adult stage were due to variation in correlation coefficient reported rather than to a much smaller numbers of replicate.

For Aarea, results were consistent with a positive correlation with RGR at seedling stage. However, no conclusion can be drawn about a change along plant stages; only four correlation coefficients were reported for this trait, and three of them were measured at the seedling stage (Fig. \ref{fig:fig3} e).

\subsection*{Results from a more complete dataset}

We also reported results from a more complete dataset to determine if additional data could reinforce some of our conclusions. This ''complete'' dataset included correlations measured with both absolute and relative growth rate (Fig. \ref{fig:fig4}), across at least two species, and did not required any control for the source of trait or growth (i.e. both could be measured on different stages) and for the environemental conditions. This release of criteria enlarged in a considerable extent the number of replicates ($n = 216$).

The ''complete'' dataset generated similar effect sizes to those reported above for SLA, WD, Hmax and seed mass, and led to similar conclusions (Fig. \ref{fig:fig4}). For Aarea, additional replicates from the ''complete'' dataset allowed to compare the effect size across plant stage. The results were consistent with a positive correlations with RGR across adult and seedling stages (Fig \ref{fig:fig4} e; CI not overlapping zero).

The comparison of Aarea effect size between "ideal" (Fig. \ref{fig:fig3} d) and "complete" (Fig. \ref{fig:fig4} d) dataset, showed no signal of an effect of stress (here mainly low light) on the correlation with RGR at seedling stage; the correlation was still positive between Aarea and RGR even when 8 correlations measured under low light conditions were added.

The comparison between RGR and AGR was possible for some trait-stage combinations. For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4} d; CI not overlapping). For both WD and Hmax, effects size measured with RGR or AGR were no differents at adult stage; CI were overlapping despite equal sample size (Fig \ref{fig:fig4} b and c).

New replicates from the complete dataset were not equally distributed across all trait-stage combinations. Some trait-stage combinations already well studied got even more support (e.g. from 25 to 59 correlation coefficients reported for SLA at seedling stage), but other still had few replicates. Thus, on the 13 traits-stage combinations studied in total, six were only supported by five or less correlations coefficient (i.e. WD-seedling, Hmax-sapling, Hmax-seedling, Seed mass-sapling, Aarea-adult and Aarea-sapling).

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results.

@@

@@

For WD the meta-analysis showed negative correlation with RGR across all plant stages, as previously reported from individual studies \citep{Wright:2010tp,Ruger:2012jv}. It should be noted however that there are few data available to test this proposition at seedling stage (n=2-5). In our model (Appendix \ref{sec:growth}) cheaper stem construction is responsible for the predicted negative correlation. Lower xylem conductance and associated lower photosynthetic potential have also been suggested \citep[reviewed by][]{Chave:2009iy}.

@@

Meta-analysis showed a positive correlation between Hmax and RGR for adult stage, but not for saplings and seedlings. The trend for tall stature species to grow faster at a given tree size than small stature species has been noted across several tree size classes and forest types (e.g. \citealt{Thomas:1996do,Poorter:2008iu,Wright:2010tp,Herault:2011dd,Ruger:2012jv,Iida:2014ep}). In \citet{Wright:2010tp}, Hmax was considered a weak predictor of growth rates of saplings; however it was the strongest predictor of growth rates of large trees. \citet{Poorter:2008iu} speculated that the Hmax-RGR relationship among large trees might arise from including small tree species with maximum size not much larger than the 10cm dbh lower threshold used to define large trees. In our growth equations, Hmax affects growth via the fraction of energy diverted to reproduction. At a given tree size, species closer to their Hmax are expected to be allocating relatively less to vegetative growth. However this applies only at sizes where some of the species have begun to reproduce, and should not affect sapling and seedling growth rates. While our results are consistent with this pattern, a doubt arise about the absence of correlation between growth and Hmax for small plant stature, due to the limited number of replicates for both saplings (n=4) and seedling stages (n=1).

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stage recoded in original publications, compared to standardised thresholds used in the analysis. Panels are for
a) age, b) height and c) diameter. Horizontal line segments indicate the size range (max., min.) for the plants used to measure growth. Study IDs correspond to the reference number in our dataset. Colours denote stage information given by the authors. The solid vertical lines indicate the thresholds used in our analysis. "*" indicated when a stage reassignment is needed. "+" on left side of the graph indicate cases where plants came from different growth form.}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with plant stage and trait. Plots show the effect size (+ 95\%CI) for the average correlation across species, by plant stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the model including stage effect fitted the data better than the null model. Results shown are from the ideal dataset (see methods for details).}
\label{fig:fig3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along plant stage. The legend is identical to Fig 3, with two exceptions. i) Results shown are from the "complete" dataset (see methods for details). ii) Likelihodd Ratio Tests were calculated on effect size combining RGR and AGR exclusively.}
\label{fig:fig4}
\end{figure}
